---
title: "R Refresh"
author: "Andrea Fox"
date: "September 6, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages
```{r}
library(readxl)
library(ggplot2)
library(dplyr)
library(pastecs)
```

## 1 - Import, Plot, Summarize, and Save Data

```
For this question I first loaded in the libraries I was going to need. Then I read in the excel file that I planned on using to work with from the US Bureau of Labor Statistics. I cannot seem to find the link for the dataset I used. I had a hard time finding a file to work with at first, but ended up using Quarter 1 2020 wage data for Agriculture, Forestry, and Fishing. 
```

### Load in data
```{r}
df <- read.csv('q12020.csv')
```

### Snippet of data to verify loaded correctly
```{r}
head(df)
```

### List of variables
```{r}
ls(df)
```

### Summarize variables
#### Month 1
```{r}
stat.desc(df$month1_emplvl)
```
#### Month 2
```{r}
stat.desc(df$month2_emplvl)
```
#### Month 3
```{r}
stat.desc(df$month3_emplvl)
```

### Plots
#### Industry code
```{r df$industry_code, echo=FALSE}
plot(df$industry_code)
```

#### Total quarterly wages
```{r df$total_qtrly_wages, echo=FALSE}
plot(df$total_qtrly_wages)
```

```
After this I saved to csv by doing write.csv(df, 'df_q12020.csv'). I would have added this as a code chunk, but for some reason I'm sturgglign with markdown today and it isn't always putting the output correctly.
```

## 2 - Explore Some Bivariate Relations

### Read in file again
```{r}
df1 <-read.csv('q12020.csv')
```

### Head()
```{r}
head(df1)
```

### Bivariate Relations
#### Month 1 to Month 2
```{r}
cor.test(df1$month1_emplvl, df1$month2_emplvl, method=c("pearson", "kendall", "spearman"))
```
#### Month 2 to Month 3
```{r}
cor.test(df1$month2_emplvl, df1$month3_emplvl, method=c("pearson", "kendall", "spearman"))
```

#### Month 1 to Month 3
```{r}
cor.test(df1$month1_emplvl, df1$month3_emplvl, method=c("pearson", "kendall", "spearman"))
```

## 3 - Organize a Data Report

### Summary of data
```{r}
summary(df)
```

### Structure of data
```{r}
str(df)
```


## Results
```
1.	The mean, median, and correlation between month 1, month 2, and month 3 employment levels were very close. For this I can see there really wasn’t much change between the three although month 2 had the highest mean at 9.906.
2.	Looking at the p-values for each of the bi-variate relationships they showed me that the null hypothesis would be rejected for each one.
3.	Looking at the standard deviations for the months all of them are around the 3.6 - 3.7 range. This means that it is 3.7 to the right of the mean. For normal distribution this would mean it is on the right tail from the middle.
4.	Looking at the summary and structure of the data if I had planned to use this for a project I would most likely be creating a few subsets of the whole data. I think this would be too much to work with all at once having 42 variables, and just glancing through I don’t think all of them would be relevant to my end problem or hypothesis.
```


